%-------------------------
% Resume in Latex (Neat and Readable)
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage[empty]{fullpage}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5} % For icons
\setlength{\tabcolsep}{0in}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\raggedright

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\bfseries\large
}{}{0em}{}[\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumePOR}[3]{
  \item{
    \textbf{#1} \hfill {#3} \\
    {#2}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item{
    \textbf{#1} \hfill {#4} \\
    {#2} \\
    {#3}
  }
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%
\begin{document}
%----------HEADING-----------------
%----------HEADING-----------------
\begin{center}
    \textbf{\Huge Mohammed Meehad Ali} \\ 
    Full Stack Developer \\
    \href{mailto:mohammedmihad2@gmail.com}{\raisebox{-0.2\height}{\faEnvelope}\ mohammedmihad2@gmail.com} \quad
    \href{tel:+918848170741}{\raisebox{-0.2\height}{\faPhone}\ +91-8848170741} \\ \quad
    \href{https://github.com/Meehad}{\raisebox{-0.2\height}{\faGithub}\ github.com/Meehad} \quad
    \href{https://www.linkedin.com/in/mohammed-mihad/}{\raisebox{-0.2\height}{\faLinkedin}\ linkedin.com/in/mohammed-mihad}
\end{center}

%-----------CAREER OBJECTIVE-----------
\section{\textbf{Career Objective}}
\small{
    I aspire to become a full-stack developer. I am dedicated to continuous learning and always seeking opportunities to enhance my skills, making me a motivated and promising candidate for a career in full-stack development.
}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Applications}{Al Jamia Arts and Science, Poopalam}{}{2021-24}
    \resumeSubheading
      {High School and Higher Secondary School}{International Indian School, Jeddah}{}{2007-21}
\resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{\textbf{Professional Experience}}
\resumeSubHeadingListStart
    \resumeSubheading
      {Full Stack Web Developer – Team Dotco}{}{Developed and maintained web applications using React.js and Django. Utilized Git for version control.}{June 2024 – July 2024}
      
    \resumeSubheading
      {Marketing Head – Xinnovate Kerala 2024}{}{Managed social media handles, developed partnerships, and coordinated campaigns.}{June 2024 – July 2024}
      
    \resumeSubheading
      {Intern – Kerala Development and Innovation Strategic Council (K-DISC)}{}{Mentored innovators, managed registrations for the Young Innovators Program, and organized events.}{June 2023 – July 2024}
      
    \resumeSubheading
      {Founder and Campus Lead – Mulearn Campus Chapter at AJAS}{}{Established the Mulearn campus chapter, networked with students, and organized events to improve campus activities.}{July 2023 – April 2024}
      
    \resumeSubheading
      {Founder and Campus Lead – AJAS Coding Club}{}{Led bootcamps, tech fests, and workshops to enhance coding education.}{November 2022 – April 2024}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
     \item \textbf{Languages}: C, Python, Javascript, Dart
     \item \textbf{Web Dev Tools}: VSCode, Git, GitHub, Postman
     \item \textbf{Frameworks}: Django, Flutter, ReactJS
     \item \textbf{Cloud/Databases}: MySQL, PostgreSQL, Firebase, MongoDB
     \item \textbf{Relevant Coursework}: Data Structures \& Algorithms, Operating Systems, Object-Oriented Programming, Database Management Systems
     \item \textbf{Areas of Interest}: Backend development, Problem solving, IoT, Product design
     \item \textbf{Soft Skills}: Problem Solving, Self-learning, Presentation, Adaptability
    }
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{\textbf{Achievements}}
\resumeSubHeadingListStart
    \resumePOR{Poster Presentation Winner}{Won 1st edition of FOSSCLT by ICFOSS, published in their academic magazine.}{2023}
    
    \resumePOR{2nd Runner-up Mentor – Xploria Women Hackathon}{Mentored team to 2nd runner-up at Xploria Hackathon.}{2023}
    
    \resumePOR{Winner – Idea Pitching Contest}{Won idea pitching contests at ISS and MES Valancherry.}{2023}
    
    \resumePOR{Runner-up – Tech Exhibition}{Finished as runner-up in tech exhibition at Christ Engineering College.}{2023}
    
    \resumePOR{Runner-up – Coding Competition}{Finished as runner-up in coding competition at Devagiri College.}{2023}
    
    \resumePOR{Top Registration for YIP 5.0}{Completed the most registrations in Malappuram district for YIP 5.0.}{2023}
\resumeSubHeadingListEnd

\end{document}
